Numerical trajectory patterns of floating macroalgae

### 2020-09-21 thesis_chapter_3.Rmd
chapter 3, map and and general additions/modifications

```{r map}

@@

@@

>>>>

```{r map, message=FALSE, warning=FALSE, include=FALSE}

@@

```{r message=FALSE, warning=FALSE}

@@

trac_map_passive <- ggplot(data = south_africa_coast_hi_res) +
geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
            size = 1.0, colour = "black", fill = NA) +
  geom_point(data = p_particle, aes(x = lon, y = lat), color = "red") +
  #geom_label(data = study_sites_edit, aes(x = lon, y = lat, label = site), nudge_x = 0, nudge_y = 0) +
  geom_rect(data = south_africa_coast_hi_res,aes(xmin=18.10, xmax=18.50, ymin=-33.70, ymax=-34.50), inherit.aes = FALSE, fill = "blue", alpha = 0.01) +
  geom_rect(data = south_africa_coast_hi_res,aes(xmin=18.40, xmax=18.90, ymin=-34.00, ymax=-34.50), inherit.aes = FALSE, fill = "red", alpha = 0.01) +
  #annotate("text", label = "Warm\nTemperate", x = 18.7, y = -34.5, size = 4.0, angle = 0, colour = "black") +
  #annotate("text", label = "Cool\nTemperate", x = 18.0, y = -34.0, size = 4.0, angle = 0, colour = "black") +
  annotate("text", label = "FALSE\nBAY", x =18.65, y = -34.25, size = 4.0, angle = 0, colour = "black") +
  scaleBar(lon = 17.8, lat = -34.45, distanceLon = 10, distanceLat = 10, distanceLegend = -10, dist.unit = "km",
  arrow.length = 10, arrow.distance = 15, arrow.North.size = 3) +
  coord_cartesian(xlim = c(17.75, 19.15), ylim = c(-32.50, -34.55)) +
  #theme(axis.ticks = element_blank()) + # Remove tick marks
  xlab("Latitude") +
  ylab("Longitude")
